---
title: 'JHU Coursera Datatools Course Project'
author: Autoz
date: '`r format(Sys.Date())`'
slug: jhu-coursera-datatools-course-project
categories: [R]
tags: [R, DataScience, R Markdown]
output:
  html_document:
    toc: yes
    keep_md: yes
    number_sections: yes
    theme: readable
editor_options: 
  chunk_output_type: console
---

> JHU DataScience Specialization/Cousers The Data Scientist’s Toolbox/Week??/Course Project

# Datatools Course Project 数据科学工具

由于这个非常入门的课程，共4Week每周一个小quiz，这个应该是最后的Project忘记了
主要是熟练掌握一些R语言的数据处理工具例如 xlsx,XML等格式，以及readr这些有用的R包用法
以下代码下载资源比较大暂不执行有兴趣的读者可以自己尝试

```{r init,echo=F,warning=F,message=F}
knitr::opts_chunk$set(cache =T, autodep =T)
pacman::p_load(tidyverse,data.table,knitr,pander,rJava,xlsx,xlsxjars,XML,magrittr,microbenchmark)
panderOptions("table.style","rmarkdown")
```

## 读取csv格式 2006年美国社区调查（ACS）

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

- (pid, Population CSV file)
- (hid, Household CSV file)

[说明书 PUMS](https://www.nber.org/acs/PUMS/README)
[说明书 DATA DICTIONARY - 2006 HOUSING](https://www.nber.org/acs/PUMS/2006/PUMSDataDict06.txt)
[PDF](https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf)

```{r read PUMS,eval=FALSE}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
download.file(fileUrl,destfile = "Fss06pid.csv",method = "libcurl")
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"
download.file(fileUrl,destfile = "Fss06hid.csv",method = "libcurl")
```


### 读取几十上百m的数据算大文件，运算应该考虑花销

```{r bechmark PUMS,echo=F,warning=F,message=F}
# 对比HID数据速度，fread读取速度非常快
A = print(microbenchmark(PID <- fread(file = "Fss06pid.csv",fill = T),
               read_csv(file = "Fss06pid.csv"),
               read.csv(file = "Fss06pid.csv"),
               times = 1))

B = print(microbenchmark(HID <- fread(file = "Fss06hid.csv",fill = T),
               read_csv(file = "Fss06hid.csv"),
               read.csv(file = "Fss06hid.csv"),
               times = 1))

PID <- as.tbl(PID)
HID <- as.tbl(HID)
C = print(microbenchmark(tapply(PID$pwgtp15, PID$SEX, mean),
               sapply(split(PID$pwgtp15,PID$SEX),mean),
               mean(PID[PID$SEX==1,]$pwgtp15),
               mean(PID$pwgtp15,by=PID$SEX),
               median(PID$pwgtp15,by=PID$SEX),
               mean(PID[PID$SEX==1,]$SERIALNO),
               median(PID[PID$SEX==1,]$SERIALNO)))
```

```{r show PUMS}
pander(arrange(A,mean))
pander(arrange(B,mean))
```

### 简单计算求和时间

```{r show MEAN}
pander(arrange(select(C,expr,mean),mean))
```

### Quiz 1

How many housing units in this survey were worth more than $1,000,000?

- 159
- 164
- **53**
- 24

## 读取xls,xlsx格式 美国国家天然气采购计划

[说明书 Natural Gas Acquisition Program](https://catalog.data.gov/dataset/natural-gas-acquisition-program)


```{r read NGAP,eval=F}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx"
download.file(fileurl,destfile = "gov_NGAP.xlsx",mode='wb')
```

```{r show NGAP}
NGAP <- read.xlsx(file="gov_NGAP.xlsx",
                  sheetIndex=1,
                  colIndex=7:15,
                  rowIndex = 18:23,
                  header=T)
NGAP <- as.tbl(NGAP)
pander(head(NGAP))
cat("Sum of Zipcode and")
sum(NGAP$Zip*NGAP$Ext,na.rm=T)
```

### Quiz 3

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called:

What is the value of:

sum(dat\(Zip*dat\)Ext,na.rm=T)

(original data source: http://catalog.data.gov/dataset/natural-gas-acquisition-program)

1. **36534720**
2. 338924
3. 33544718
4. 0

## 读取xml格式 巴的摩尔餐厅数据

[说明书 data.baltimorecity.gov](https://catalog.data.gov/dataset/restaurants-15baa)

```{r read Frestaurants,eval=F}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
download.file(fileUrl,destfile = "Frestaurants.xml",mode='wb')
```

```{r show Frestaurants}
system.time(DOC <- xmlTreeParse("Frestaurants.xml", useInternal = TRUE))
rootNode <- xmlRoot(DOC)
# 邮编是"21231" 的记录有多少条
sum(xpathSApply(rootNode, "//zipcode", xmlValue) == "21231")
```

### Quiz 4

How many restaurants have zipcode 21231?

- **127**
- 17
- 28
- 156


<center>**THE END**</center>
